Context-dependent consequences of including lagged effects in demographic models

### 2022-05-26 docs/paper.Rmd
fixed up lifecycle diagram to include rendered equations

```{r aic, results='asis'}
pandoc.table(
  tar_read(aic_tbl_df),
  justify = c("left", "left", "left", "right", "right", "right"),
  full_width = FALSE,
  caption = "(\\#tab:aic) Comparison of vital rate models for deterministic, stochastic kernel-resampled, and stochastic parameter-resampled IPMs. 'edf' is the estimated degrees of freedom of the penalized GAM."
)
```

@@

```{r lifecycle}
#| fig.cap = "Diagram of IPMs with equations"

# Draft of this figure is in docs/figures/Heliconia lifecycle DAG.key
knitr::include_graphics(here::here("docs", "figures", "lifecycle.png"))
```

Combine above figure with this table:

| Description                                  | Deterministic    | Stochastic, kernel-resampled | Stochastic, parameter-resampled (DLNM) |
|--------------------|------------------|------------------|------------------|
| Mature plant survival                        | $s(z)$           | $s_y(z)$                     | $s(z;\theta_{0-36})$                   |
| Seedling survival                            | $s_0$            | $s_{0_y}$                    | $s_0(\theta_{0-36})$                   |
| Mature plant growth or regression            | $G(z^\prime, z)$ | $G_y(z^\prime,z)$            | $G(z^\prime,z;\theta_{0-36})$          |
| Seedling growth into mature plant            | $G_0(z^\prime)$  | $G_{0_y}(z^\prime)$          | $G(z^\prime;\theta_{0-36})$            |
| Probability of flowering                     | $p_f(z)$         | $p_{f_y}(z)$                 | $p_f(z;\theta_{0-36})$                 |
| Size-specific fecundity                      | $f(z)$           | $f(z)$                       | $f(z)$                                 |
| Probability of germination and establishment | $g$              | $g$                          | $g$                                    |

<!--# probably can't make the figure with the table in it in R easily. -->

\
\
Just playing with something here.
This is the population trajectories from the iterated IPMs with `normalize_pop_size=FALSE`.
I thought maybe I'd be able to see some (lagged) similarities between the kernel sampled and DLNM IPMs because they are run with the same sequence of years.
Nothing obvious pops out.
Not sure this figure is worth including.

>>>>

```{r aic, results='asis'}
pandoc.table(
  tar_read(aic_tbl_df) %>% rename("edf" = "df"),
  justify = c("left", "left", "left", "right", "right", "right"),
  full_width = FALSE,
  caption = "(\\#tab:aic) Comparison of vital rate models for deterministic, stochastic kernel-resampled, and stochastic parameter-resampled IPMs. 'edf' is the estimated degrees of freedom of the penalized GAM."
)
```

@@

```{r lifecycle}
#| fig.cap = "Lifecycle diagram of IPMs with equations.  Diagram shows equations for the deterministic IPM and the table shows how the equations differ in the other two IPM types."

# Draft of this figure is in docs/figures/Heliconia lifecycle DAG.key
knitr::include_graphics(here::here("docs", "figures", "lifecycle.pdf"))
```

<!-- Just playing with something here. This is the population trajectories from the iterated IPMs with `normalize_pop_size=FALSE`. I thought maybe I'd be able to see some (lagged) similarities between the kernel sampled and DLNM IPMs because they are run with the same sequence of years. Nothing obvious pops out. Not sure this figure is worth including. -->
